Lhyra: Learned HYbrid Recursive Algorithms

### 2019-05-16 paper/main.tex
paper formatting updates

\documentclass{article}
\usepackage{hyperref, graphicx, floatrow}

\usepackage[letterpaper, margin=1in]{geometry}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}

@@

We would also like to investigate Lhyra's effectiveness at optimizing criteria other than time. One option would be to explore polynomial time approximation algorithms to NP-hard problems. In this scenario, cost could be a weighted function of evaluation time and accuracy, depending on the priorities of the user. It is also likely that for these more difficult problems, the benefits of Lhyra could be far greater in magnitude than they are in \textsc{Sorting} and \textsc{Closest Pair}, because optimization for time on already-fast problems constrains the types of features and complexity of optimizer that Lhyra can use. For problems relating to protein-folding, for example, Lhyra could use more complex features, models, and solvers, and operate on more diverse data distributions, and possibly yiled big gains for a problem which is useful and hard.

>>>>

\documentclass[11pt]{article}
\usepackage{hyperref, graphicx, floatrow}

\usepackage[letterpaper, margin=1.25in]{geometry}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}

@@

We would also like to investigate Lhyra's effectiveness at optimizing criteria other than time. One option would be to explore polynomial time approximation algorithms to NP-hard problems. In this scenario, cost could be a weighted function of evaluation time and accuracy, depending on the priorities of the user. It is also likely that for these more difficult problems, the benefits of Lhyra could be far greater in magnitude than they are in \textsc{Sorting} and \textsc{Closest Pair}, because optimization for time on already-fast problems constrains the types of features and complexity of optimizer that Lhyra can use. For problems relating to protein-folding, for example, Lhyra could use more complex features, models, and solvers, and operate on more diverse data distributions, and possibly yield big gains for a problem which is useful and hard.
